---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sgroupr)
```

## Introduction

This Sgroupr package is built to use/apply some of the finite abelian groups. You can find more information through this link: https://en.wikipedia.org/wiki/List_of_small_groups. 

Two vignettes are contained inside this package. One of them is created to explain how to use the `vtcrs` package based on an example from the finite abelian group. The second vignette described in details how to use the `sgroupr` package. It would be best to first familiarize yourself with the use of the vtcrs package and then read this vignette to understand how to work with the sgroup package.

## Inside each group

For this section, we will use Klein_8 as a reference to demonstrate/illustrate how we built each group.
To minimize errors and to facilitate the use of the package, each group (element) contains 3 different functions/code to be utilized by the users.

The first function allows the users to see the first row of the matrix following a specific group(element of a group). 
`Klein_8` as an example an element of the Klein group with a length from 0 to 7. This first function therefore output a sgroupr_sgpr object following Klein_8 based on the given values. 

```{r}
Klein_8(0:7)
Cyclic_4(0:3)
```
The goal of the second function is to help users checking if a sgroupr_sgpr object belongs or not to the specified group.
The output should therefore be TRUE or FALSE depending on the value inserted as an input. Based on the example used below, we can see that the function returns TRUE for y and FALSE for u.

```{r}
# Correct Choice
y <- Klein_8(0:7)
is_Klein_8(y)
#Incorrect choice
u <- Cyclic_16(0:15)
is_Klein_8(u)
```
The last function allows users to transform numeric/integer value to the specific group. As shown below, the vector containing values from 0 to 7 changes the type of the values inserted.

```{r}
x <- c(0:7)
# x is an integer vector
str(x)
#After using as_Klein_8, it changes to Klein_8
str(as_Klein_8(x))
```

## There are total 20 different groups that can be use in our sgroup package and each group correspond to one Cayley table. The following shows the group name and its funcion to create the group:

### Group name - Function name in sgroup package - The length limitation of function

#### Cyclic Group
cyclic group C3 - `Cyclic_3` `as_Cyclic_3`     - 0:2
cyclic group C4 - `Cyclic_4` `as_Cyclic_4`     - 0:3
cyclic group C6 - `Cyclic_6` `as_Cyclic_6`     - 0:5
cyclic group C8 - `Cyclic_8` `as_Cyclic_8`     - 0:7
cyclic group C12 - `Cyclic_12` `as_Cyclic_12` - 0:11
cyclic group C16 - `Cyclic_16` `as_Cyclic_16` - 0:15

#### Klein Group
Klein group K4 - `Klein_4` `as_Klein_4` - 0:3
Klein group K8 - `Klein_8` `as_Klein_8` - 0:7

#### Multiplication Group
group C3xC2 - `C3_C2` `as_C3_C2` - 0:5
group C4xC2 - `C4_C2` `as_C4_C2` - 0:7
group C4xC3 - `C4_C3` `as_C4_C3` - 0:11
group C6xC2 - `C6_C2` `as_C6_C2` - 0:11
group K4xC3 - `K4_C3` `as_K4_C3` - 0:11
group C4xC4 - `C4_C4` `as_C4_C4` - 0:15

#### Dihedral Group
symmetric group S3,dihedral Dih6 (triangle) - `Dih_6` `as_Dih_6`            - 0:5
dihedral group Dih8 (square) - `Dih_8_square` `as_Dih_8_square`             - 0:7
dihedral group Dih8 (Heisenberg) - `Dih_8_heisenberg` `as_Dih_8_heisenberg` - 0:7
dihedral group Dih12 - `Dih_12` `as_Dih_12`                                 - 0:11


Here are the steps that we can use on the group function in the sgroup package. We use cyclic group C8 as an example.

# 1.Use `Cyclic_8()` to create a Cyclic_8 group. The limitation of group length is the maximum group number - 1 
```{r}
x <- Cyclic_8(0:7)
x
```

# Or you can use `as_Cyclic_8()` to create a Cyclic_8 group. The difference is you can use the character inside `as_Cyclic_8()`
```{r}
as_Cyclic_8(0:7)
as_Cyclic_8(c("0","1","2","3","4","5","6","7"))
```

# 2.We can use `group()` to check the group name 
```{r}
group(x)
```

# 3.Use `table()` to see the Cayley table of the particular group
```{r}
table(x)
```

# 4.Use can use + operation to do the arithmetic for the group, and based on the number we use, it will return the number + 1 row of the Cayley table. When the number is greater than the total row number, it just starts from the first row.
```{r}
5 + x # it should return row 6 of the Cayley table 

11 + x # it should return row 4 ((11 %% 8) + 1) of the Cayley table 
```
