---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(sgroupr)
```

## Introduction

This Sgroupr package is built to use/apply some of the finite abelian groups. You can find more information through this link: https://en.wikipedia.org/wiki/List_of_small_groups. 

Two vignettes are contained inside this package. One of them is created to explain how to use the `vtcrs` package based on an example from the finite abelian group. The second vignette described in details how to use the `sgroupr` package. It would be best to first familiarize yourself with the use of the vtcrs package and then read this vignette to understand how to work with the sgroup package.

There are total 20 different groups that can be use in our sgroup package and each group corresponds to one Cayley table. The following shows the group name and its function to create the group:

### Group name - Function name in sgroup package - The length limitation of function

#### Cyclic Group
- cyclic group C3 - `Cyclic_3` `as_Cyclic_3`     - 0:2
- cyclic group C4 - `Cyclic_4` `as_Cyclic_4`     - 0:3
- cyclic group C6 - `Cyclic_6` `as_Cyclic_6`     - 0:5
- cyclic group C8 - `Cyclic_8` `as_Cyclic_8`     - 0:7
- cyclic group C12 - `Cyclic_12` `as_Cyclic_12` - 0:11
- cyclic group C16 - `Cyclic_16` `as_Cyclic_16` - 0:15

#### Klein Group
- Klein group K4 - `Klein_4` `as_Klein_4` - 0:3
- Klein group K8 - `Klein_8` `as_Klein_8` - 0:7

#### Multiplication Group
- group C3xC2 - `C3_C2` `as_C3_C2` - 0:5
- group C4xC2 - `C4_C2` `as_C4_C2` - 0:7
- group C4xC3 - `C4_C3` `as_C4_C3` - 0:11
- group C6xC2 - `C6_C2` `as_C6_C2` - 0:11
- group K4xC3 - `K4_C3` `as_K4_C3` - 0:11
- group C4xC4 - `C4_C4` `as_C4_C4` - 0:15
- group C8xC2 - `C8_C2` `as_C8_C2` - 0:15
- group Q8xC2 - `Q8_C2` `as_Q8_C2` - 0:15

#### Dihedral Group
- symmetric group S3,dihedral Dih6 (triangle) - `Dih_6` `as_Dih_6`            - 0:5
- dihedral group Dih8 (square) - `Dih_8_square` `as_Dih_8_square`             - 0:7
- dihedral group Dih8 (Heisenberg) - `Dih_8_heisenberg` `as_Dih_8_heisenberg` - 0:7
- dihedral group Dih12 - `Dih_12` `as_Dih_12`                                 - 0:11

Here are the steps that we can use on the group function in the sgroup package. We use cyclic group C8 as an example.

#### 1. Use `Cyclic_8()` to create a Cyclic_8 group. The limitation of group length is the maximum group number - 1 
```{r}
x <- Cyclic_8(0:7)
x
```

#### Or you can use `as_Cyclic_8()` to create a Cyclic_8 group. The difference is you can use the character inside `as_Cyclic_8()`
```{r}
as_Cyclic_8(0:7)
as_Cyclic_8(c("0","1","2","3","4","5","6","7"))
```

#### 2. Use `is_Cyclic_8()` to check whether the object belongs to the Cyclic_8 group. 
```{r}
is_Cyclic_8(x)
```

#### 3. If you want to double check, you can use `group()` to check the group name 
```{r}
group(x)
```


#### 4. You also have the possibility to check the number of a specific group. Dihedral 6 should only have 6 numbers based on its cayley table with maximum be 5. If an user inputs more than 5 numbers, those numbers should be NA.

```{r}
check_number(0:5, group = "Dih_6")
check_number(0:6, group = "Dih_6")
```

#### 5. If it is also possible to verify if a specific group is inside the sgroupr package. If user inputs something not included, it should throws an error. 
```{r}
check_group("Klein_4")
```

#### 6. You can implicitly change the type of an object (Coercion)
```{r}
x <- Dih_6(0:5)
vctrs::vec_c(x,1L)
vctrs::vec_c(x,x)
vctrs::vec_c(1L,x)
vctrs::vec_c(6L,x)
```

#### 7. Or you can change the type of the object explicilty (Casting)
```{r}
x
vctrs::vec_cast(x,integer())
vctrs::vec_cast(c(1L,2L,3L,4L,5L), sgrp(group = "Dih_6"))
```


#### 8. Use `table()` to see the Cayley table of the particular group
```{r}
table(x)
```

#### 9. Use can use + operation to do the arithmetic for the group, and based on the number we use, it will return the number + 1 row of the Cayley table. When the number is greater than the total row number, it just starts from the first row. There are three different way to do the arithmetic:

1. number + group
```{r}
x <- Cyclic_8(0:7)

5 + x # it should return row 6 of the Cayley table 

11 + x # it should return row 4 ((11 %% 8) + 1) of the Cayley table 
```

2. group + number
```{r}
x + 5

x + 11 
```

3. group + group
```{r}
z <- Cyclic_8(5)

x + z
```

